Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 overall.tex
Run 3 --> 2 fix (minor, local).

During the experiment time window, about 2.25M detector simulation jobs were
completed on Titan, for a total of 225M events processed. This is equivalent to
0.9\% of all the 250M detector simulations performed by ATLAS in the same period
of time, and 3.5\% of the 6.6B events processed by those jobs. Comparatively,
Titan contributed 3.9\% of the total of around 200K cores available to ATLAS on
Grid, Cloud, and HPC infrastructures together. These figures confirms the
relevance of supercomputers' resource contribution to the LHC Run 3, especially
when accounting for the amount of unused backfill availability and the rate of
improvement of PanDA efficiency.

>>>>

During the experiment time window, about 2.25M detector simulation jobs were
completed on Titan, for a total of 225M events processed. This is equivalent to
0.9\% of all the 250M detector simulations performed by ATLAS in the same period
of time, and 3.5\% of the 6.6B events processed by those jobs. Comparatively,
Titan contributed 3.9\% of the total of around 200K cores available to ATLAS on
Grid, Cloud, and HPC infrastructures together. These figures confirms the
relevance of supercomputers' resource contribution to the LHC Run 2, especially
when accounting for the amount of unused backfill availability and the rate of
improvement of PanDA efficiency.
